\vspace{-0.05in}

\section{Related Research}
\label{sec:Related_Research}

In recent years, much of the proliferating work in the development of mission-critical distributed real-time systems addresses the need for Safety and Verification-driven Engineering. Structural properties of the system are established using domain-specific modeling tools. Design models are transformed into relevant analysis models to study probable behaviors of the system and identify anomalies. When analyzing timing behavior, typically several exaggerated assumptions are made about the system behavior. These include upper bounds on task execution times, service rates, maximum resource consumption etc. The results of system analysis using such assumptions are equally pessimistic. However, real-time systems with high criticality necessitate such pessimistic assumptions to avoid the consequences of poor design. Predictability of system behavior is achieved by obtaining upper bounds of the system properties.   

Petri nets and their extensions have proven to be a powerful formalism for modeling and analyzing concurrent systems. System designs represented using a domain-specific modeling languages are often translated into Petri nets for formal analysis. High-level formalisms such as AADL models have been translated into Symmetric nets for qualitative analysis \cite{kordon_sn} and Timed Petri nets \cite{kordon2009} to check for real-time properties such as deadline misses, buffer overflows etc. Similar to \cite{kordon2009}, our CPN-based analysis also makes use of observer places \cite{Alpern1989} that monitor the system behavior and look for real-time property violations and prompt completion of operations. However, \cite{kordon2009} only considers periodic threads in systems that are not preemptive. Our analysis covers a broader range of thread interaction patterns geared towards component-based applications operating on a hierarchical scheduling scheme requiring higher-level modeling concepts to capture component interaction in a distributed setup. 

%\AD{since you are discussing hierarchical scheduling here - you should describe the system or the framework briefly in the introduction.}

In the context of component-based systems, for complete real-time analysis, it is necessary to obtain significant information about the component assembly, the interaction patterns and real-time data about the temporal behavior of components. The real-time model of the system is composed of real-time models of its constituent parts, each with its own temporal behavior. Using abstract model descriptors, \cite{Lopez2006} describes a real-time model for component-based systems, including semantic and quantitative meta-data about component real-time behavior. Using the MAST transactional modeling methodology \cite{MAST1, MAST2} and analysis tools in the MAST environment, schedulability checks and priority assignment automation are performed. It must be noted here that for every real-time application, a separate and independent real-time analysis model is generated for each mode of operation and analyzed separately.

%Several analysis approaches present tool-aided methodologies that exploit the capabilities of existing analysis and verification techniques. In the verification of timing properties of composed systems, \cite{medina2011} uses the OMG UML Profile for Modeling and Analysis of Real-Time and Embedded Systems (MARTE) modeling standard with model transformations to convert design models into MAST output models for concrete schedulability analysis. In a similar effort, AADL models are translated into real-time process algebra \cite{sokolsky2006} reducing schedulability analysis into a deadlock detection problem searching through state spaces and providing failure scenarios as counterexamples.

%In order to analyze hierarchical component-based systems, the real-time resource requirements of higher-level components need to be abstracted into a form that enables scalable schedulability analysis. The authors in \cite{easwaran2006} present an algorithm where component interfaces abstract the minimum resource requirements of the underlying components, in the form of periodic resource models. Using a single composed interface for the entire system, the component at the higher level selects a value for operational period that minimizes the resource demands of the system. Such refinement is geared towards minimum waste of system resources. 

For classes of component-based systems whose component assembly and application structure change dynamically over time, design-time verification is observed to be insufficient. Incremental re-verification strategies \cite{johnson2013} have been applied on dynamic systems to augment traditional compositional verification by identifying the minimal set of components that require re-verification after dynamic changes. Since our approach considers design-time deployment plans that are static, the analysis does not consider dynamic changes to component assembly at run-time. 

\vspace{-0.1in}