\begin{appendices}

\chapter{Publications}

\label{ch:publications}

The full text in each of the following papers was reviewed by at least 3 reviewers.

\section{Workshop Papers}
\nobibliography*{}
\begin{itemize}
	\item \bibentry{kumar2014colored}
	\item \bibentry{SEUS}
	\item \bibentry{SEUS2016}	
\end{itemize}

\section{Conference Papers}
\begin{itemize}
	
	\item P. Kumar, W. Emfinger, A. Kulkarni, G. Karsai, D. Watkins, B. Gasser, C. Ridgewell, and A. Anilkumar. ROSMOD: A Toolsuite for Modeling, Generating, Deploying, and Managing Distributed Real-time Component-based Software using ROS. In \textit{Proceedings of the IEEE Rapid System Prototyping}, RSP 2015, Amsterdam, Netherlands, 2015. IEEE	
	
	\item P. Kumar, W. Emfinger, and G. Karsai. A Testbed to Simulate and Analyze Resilient Cyber-Physical Systems. In \textit{Proceedings of the IEEE Rapid System Prototyping}, RSP 2015, Amsterdam, Netherlands, 2015. IEEE	
	
	\item W. Emfinger, P. Kumar, A. Dubey, W. Otte, A. Gokhale, G. Karsai. DREMS: A Toolchain for the Rapid Application Development, Integration, and Deployment of Managed Distributed Real-time Embedded Systems. In \textit{Proceedings of the IEEE Real-Time Systems Symposium}, RTSS@Work 2013, Vancouver, Canada, 2013. IEEE
	
	\item Balasubramanian, D., W. Emfinger, P. S. Kumar, W. Otte, A. Dubey, and G. Karsai. An application development and deployment platform for satellite clusters.  In \textit { Proceedings of the Workshop on Spacecraft Flight Software}, 2013
	
	\item Balasubramanian, D., A. Dubey, W. R. Otte, W. Emfinger, P. Kumar, and G. Karsai. A Rapid Testing Framework for a Mobile Cloud Infrastructure.  In \textit{Proceedings of the IEEE International Symposium on Rapid System Prototyping}, RSP, 2014. IEEE
	
\end{itemize}

\section{Journal Papers}
\begin{itemize}
	\item \bibentry{balasubramanian2015drems}
	
	\item Levendovszky, T., A. Dubey, W. R. Otte, D. Balasubramanian, A. Coglio, S. Nyako, W. Emfinger, P. Kumar, A. Gokhale, and G. Karsai. DREMS: A Model-Driven Distributed Secure Information Architecture Platform for Managed Embedded Systems. In \textit{IEEE Software}, vol. 99: IEEE Computer Society, 2014. IEEE	
\end{itemize}

\subsection{Awaiting Reviews}
\begin{itemize}
	\item P. Kumar, W. Emfinger, G. Karsai, D. Watkins, B. Gasser, and A. Anilkumar. ROSMOD: A Toolsuite for Modeling, Generating, Deploying, and Managing Distributed Real-time Component-based Software using ROS. In special issue of \textit{Journal of Electronics} on Rapid System Design with Dedicated Architectures and Specific Software Tools, 2016.
\end{itemize}

\end{appendices}

